PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-04-28 refereeResponse.txt

cript at hand presents a numerical study of planetesimal accretion. The authors identify a novel mode of accretion that operates if the primary's radius is a significant fraction of its hill-radius - a criterion the authors find to be met at short orbital periods in circumstellar disks. This new accretion mode is shown to be highly efficient, resulting in several large planetary embryos and a depletion of the primordial planetesimal formation, and is therefore distinct from bimodal planetesimal distribution that is the end product of an oligarchic growth phase.

I find the presented research to be innovative, interesting, and valuable for the scientific community. However, before I can recommend the manuscript for publication, I believe there are several areas that require improvement. Specifically, I suggest that the authors address the five major comments outlined below to ensure that the findings are properly supported and effectively communicated. I also include a detailed list of specific notes, comments and questions that I suggest the authors consider when revising the manuscript. I appreciate the authors' work and look forward to seeing the progress on the manuscript.

TODOs:
	Dont italicze math subscripts (do this for figures too)
	Discussion of Roche limit at end of section 2
	Centering of note text under table 1
	Centering of white in figure 1 colorbar (colormap on plot is correctly scaled)
	Add a note explaing why no fdLo on the collision plots
	Explanation of \tilde{b} in section 5 ok?

@@

367: I'm assuming the semi-major axis is also drawn from a uniform distribution?
	Yes, this is now clarified.

377: is alpha=1 chosen because it is the highest stable alpha? If so I would write that. Why is beta = 15000 chosen?
	Alpha = 1 corresponds to r_pl = r_hill. One would expect that gravitational scattering should completely shut off for alpha >= 1. Beta = 15,000 corresponds to <e^{1/2}>^2 = 0.05, which is the largest eccentricity for which a particle at 1 AU will an apo and pericenter distance that is still within the boundaries of the disk. For an eccentricity dispersion this large, the stirring timescale is much longer than the simulation time, so we can be confident that the boundary effects do not get worse. An explanation of the large beta value has been added to the text.

Figure.2: Some suggestions to improve this figure are:
A reference planetesimal size that shows what mass a circle has
	Added
Horizontal lines in each panel showing where e_h is
	Alongside the text describing this figure, we have added a note describing where e_h = 1 (the boundary between shear and dispersion dominated encounters) and <v^2>^{1/2} = v_esc lies in eccentricity space. These should be interpreted as rough lower and upper limits for reasonable values of the planetesimal eccentrities.
Maybe consider having beta value as a column label and alpha value as a row label. I would also explicitly state the values for alpha.
	Added
I would also probably label the four panels / cases a,b,c,d and then refer as such in the text body
	Done

391: Why would this because there are no high eccentricity planetesimals. Isn't the fact that there is no residual population not already evidence that encounters are accreting rather than scattering? Also, isn't this also not just very expected since alpha exactly quantifies the relative importance of scattering vs accretion?
	The point we were trying to make was this: Had scattering been more important than accretion, not only would there still be planetesimals left over, but they would have been moved to higher eccentricity orbits. Although in the case of small alpha, large beta, it appears as if the embryos instead cool off relative to the planetesimals. We have reworded this to say 'the lack of high eccentricity planetesimals, relative to the protoplanets'.

394: small alpha, large beta doesn't look dynamically cool to me.
	Related to the last point, this is referring to the dynamical state of the protoplanets, relative to the initial planetesimals. This has now been clarified in the text.
400: Small alpha large beta does not look dynamically cooler than large alpha large beta to me. In fact, the opposite.
	This is a mistake in the text (replaced 'latter' with 'former').
402: I don't really understand why small alpha small beta leads to so many dynamically hot bodies, both planetesimals and protoplanets. Maybe the authors can elaborate.
	Is this specifically referring to small alpha, small beta (and not small alpha, large beta)? The final eccentricities of the planetesimals and protoplanets look about the same to me.
	The small alpha disks ends up the hottest because of two effects:
		1. Less collisions overall, so less inelastic damping to remove energy
		2. Close encounters are more likely to result in a scattering event,
		which converts the overall shearing motion of the disk into random motion

Figure 3:
Again, I really think labeling the cases would be helpful.
I would express the mass in units of e.g. Ceres
	We feel that Ceres masses are a little too asteroid belt-specific. We have instead chosen to describe the masses in M_earth.
406: I'm not sure about "significantly" larger. The biggest body in large alpha, small beta is about a factor 3 more massive than in small alpha, small beta. This is only a factor of 1.4 in size.
	The text now says 'a factor of a few larger'
415: the y-label in Fig.6 does not match the description in the text
	This comment must be referring to figure 4? If so, 'm_max' in the text has been changed to 'M'.
Figure 4:
Why don't the simulations start all with m_max/m = 1?
	This is because m_max/m = 1 at T=0 and we have time plotted on a log scale. We have modified the x window of this figure so that the phase before the first snapshot (where the m_max/m values appear flat) is not visible.
I'd be interested in also having another panel that shows the evolution of just M_max and <m> (maybe in solid and dashed lines) for the four simulations. That would also underscore that the turnover is driven by an increase in <m> rather than m_max.
	We have now added a second panel to figure 4 which shows the evolution of these quantities separately. It is now clear that the turnover of the blue and orange curves on the original plot are driven by a continued increase in <m>. This is now stated in the text as well.

418: I would specifically state that for the large alpha cases runaway growth only occurs at the start, to avoid initial confusion that the slope turns around when the planetesimal supply is depleted.
	This is now stated in the text.

@@

435: Is this true? I was under the impression that the residual planetesimal population remains? I think this does not seem consistent with the rest of the work...?
	'Depleted' is maybe not the right phrase to use here. Through a combination of depletion and scattering onto high eccentricity orbits (in which gravitational focusing is almost completely supressed), the planetesimal accretion timescale should eventually become longer than the age of the system, so the rest of the population is effectively frozen out. This is now explained in the text.
446: What exactly does alpha being non-negligible mean? Given that alpha is always less than unity, what alpha value marks the transition of the oligarchic growth regime vs, consumption regime? See major comment.
	This is a good point, and I'm not sure if we have a definitive answer. I think the best thing to do here is to state the converse: for alpha << 1, most encounters result in scattering and you get oligarchic growth. The key finding from this section is that oligarchic growth does not occur when alpha is not << 1. The text has been updated to reflect this.

5. Full disk Simulation
5.1 Initial Conditions
470: Reference of TRAPPIST-1
	Added reference to Gillon 2016 + 2017, Agol 2021
483 I recommend writing Eq. (6) along the lines of 10 g/cm^2 \times A (M_*/M_\odot)(r/1AU)^(-delta) for readability. The Sigma_MMSN is never used so it's not necessary.
	Done
Table 1.
I don't think the notes are necessary
	We could use some clarification here. Is this because the variables in table 1 are already defined elsewhere in the text? Or should we incorporate the information from the notes in some other way?
I would probably put the planetesimal masses in units of Ceres
	As discussed above, we feel that Ceres masses are too asteroid-belt specific. Instead, we have chosen to display the planetesimal masses in M_earth.
I think Table 1 and Table 2 could be combined
	Table 1 has been merged into table 2.

@@

490: How could such an enhancement in planetesimal surface density be achieved initially? Is this initial condition consistent with planetesimal formation models, e.g. Dra̧żkowska & Dullemond 2018, Lenz et al 2019.
	This is briefly discussed in the introduction but we will expand upon it here. Most mechanisms involve dust traps or pressure bumps occuring at some preferential location in the disk which trigger the streaming instability. Dra̧żkowska & Dullemond 2018 show that a migrating snow line can actually trigger planetesimal formation over a fairly wide area, and also produce surface density enhancements at least as large as the ones we use. Given that low-mass stars have particularly extreme luminosity changes during the pre-main sequence (see Baraffe 2015), one can imagine that it might not be hard to trigger planetesimal formation over a wide area. This particular paragraph in the text has been expanded to discuss this.

493: What is the motivation behind variation in the power-law index? Is there significant uncertainty in the MMSN power law index?
	Chiang and Laughlin 2013 applied a similar analysis to Kepler multis and found that delta varies between 1.6 and 1.8. Sub-mm observations of cold outer disks finds power law slopes as low as 0.5 (Mundy 2000, Andrews 2009, 2010). Therefore, we vary delta by +/- 1.0 from the MMSN value. There is now a separate paragraph in the text explaining this
499: Maybe elaborate on why this equilibrium is physical? Are there other works which use the same balance to inform initial conditions?
	t_vs = t_gas is more of an upper limit on the eccentricity, although this is the same technique that Kokubo 2002 uses to set up the initial conditions. It's certainly possible that the disk could have started out dynamically colder, although as we showed in figure 2, this doesn't seem to affect the resulting protoplanets. We have added a short discussion about this to the text.
504: missing respectively. And semi-major axes.
	Fixed
505: When is the Stokes regime valid, and what does it mean?
	In the Stokes regime, the mean free path of the gas is much smaller than the size of the bodies and the gas can be treated as a fluid. For conditions in a typical protoplanetary disk, Stokes drag is relevant for cm-sized bodies and larger. This has been added to the text.
506: The letter tau is used for a timescale just above, but now it says t. I would recommend staying consistent. Tau tends to be used for dimensionless timescales, so I would probably go with t_s and t_vs.
	tau_vs has been changed to t_vs in equation 7.
511: Solid-to-gas surface density ratio of 1/240 seems very small, especially given that the authors are considering the solid surface density to already be enhanced by a factor of 100. Also, if the planetesimals are already formed, it is conceivable that the gas disk is already dissipating (especially so close in). I think the authors could be over-estimating the gas density by up to a factor of a 100, which means the stopping time would be a factor of 100 longer.
	A d/g ratio of 1/240 is the value inferred for the inner solar system using the original MMSN analysis in Hayashi 1981. However, we agree that there is a rather large range of possibilities for the actual gas surface density, given that there are no direct measurements of Sigma_gas for the inner regions of a planet-forming disk (and it isn't clear exactly when the planet formation process should start). A variation in the gas surface density of by factor of 100 could either make gas drag entirely unimportant, or act to completely remove solids from the inner disk, in which case we wouldn't be able to form any protoplanets.

	As is done by Hansen + Murray 2012, we will assume that the gas profile follows something resembling the MMSN and the various solid surface density profiles we test broadly account for the different mechanisms that might act to deliver enough solid material to the inner disk.

	These points are now discussed at the end of section 5.1
516: I suggest using another symbol for the temperature power law, since Q is associated with the Toomre value of the disk, for example q. Also, this equation should read T(r) = T_0(r/1AU)^-q, right?
	Q was changed to q to be consistent with the Andrews + Williams paper. the '/1AU' has been added to the T(r) equation.
521: Where is that equation coming from? Maybe add reference.
	This is equation 4.30 from 'Astrophysics of Planet Formation' by Phil Armitage. A reference has been added to the text.

@@

5.2. Gas Drag Force
512: I think it would be very informative to calculate the dimensionless stopping time, i.e. the Stokes number of the planetesimals, I'm assuming that they are substantially above unity, which means that the bodies are essentially decoupled from the gas.
	Agreed. Describing things in terms of the Stokes number allows us to simplify this section a bit. For the initial planetesimals, St >> 1 at both the inner and outer disk edge Because St ~ m^1/3, we can guarantee that bodies will remain decoupled from the gas throughout the simulation. By discussing the Stokes number, we can also avoid having to compare the stopping time with the integration time of the simulations. These points are now all discussed in the text.
536: Isolation mass lacks definition
	We have removed any mention of the isolation mass here. The fact that St ~ m^1/3 is enough to guarantee that the gas and solids remain decoupled.

5.3 Time-stepping Criterion
554: footnote 2 can just go in the main text body.
	Done
584: footnote 3 can also go in the main text body.
	Done
584: Are there any works on the numerical robustness of this more efficient time-stepping scheme. While I'm inclined to believe that the error is only marginal, I think having some sort of test (or a reference to one) would make the results more steadfast.
	I'm fairly certain that we are the first ones to try this. I've added an appendix that compares this timestepping scheme against a fixed timestep case. There appear to be no meaningful differences.

5.4 Results
586: Maybe include reference to figure where this is shown
	Figure 1 of Kokbubo 2002 shows this clearly. A reference to the paper has been added in the text.
592: Is this really always true? Counterexample e.g. Emsenhuber et al 2021 and others.
	The NGPPS models (along with the Clement 2020 paper) seem to be a couple of notable exceptions to this, although the embryo growth is not treated self-consistently leading up to the giant impact phase. We have added a mention of the Emsenhuber papers to the text.
Table 2:
What is the rescaled integration time?
	Because we inflated the collision cross sections by a factor of 6, the growth timescale was shortened by a factor of 36. The rescaled integration time is the actual integration time multiplied by this factor. This is explained in the note underneath the table.

@@

Figure 5:
I think the bottom panel should have a log y-axis
	TODO: I dont think this is necessary? If I make this change, do I need to do the same thing for figure 8? The way \tilde_b is defined we are already showing mass in a non-linear way.

@@

644: If I look at the contour map by eye, the eccentricity distribution doesn't seem all that different in the inner vs outer disk. Maybe the difference can be quantified?
	You are right that the variation in eccentricity is not huge. For the model used by our initial condition generator, the mean eccentricity is a factor of 4x larger at the outer disk edge, compared to the inner disk edge. This is now stated in the text.
647: This is an interesting point. I'd be interested in seeing a comparison between inner and outer disk accounting for that difference in time scales. Is it possible to include such a comparison maybe with a figure?
	Yes! See our updated version of figure 6. The time is now shown in units of the local accretion timescale, and it is now apparent that the planetesimal surface density curves all follow the same trajectory outside of about 40d. In a rather counter-intuitive fashion, planetesimals actually appear to deplete more slowly (relative to the initial planetesimal-planetesimal accretion time) at short period. The lack of gravitational scattering in the inner disk means that embryos do not exhibit any 'mass preference' in who they collide with.

@@

The authors state "indicating that accretion of planetesimals is important during all phases of the evolution", yet the smooth accreting fraction is only between 1-10% for all these bodies. Seems to me that for all bodies, regardless of mass and orbital period, major mergers are significantly more important - that is at least with the author's definition of major and minor merger.
	This statement makes a little more sense after broadening or definition of 'minor mergers' to include m < 100 m_0.
In the legend, I think "orbit" should be put in the subscript instead of P_orbit
746: This is just because in the inner disk there are no primordial planetesimals left to build the more massive bodies, right?
	After coloring the points by orbital period, its clear that this isn't the case. In the inner disk, there is a huge amount of variation in the smooth accretion fraction for a given mass. This suggests that inner disk protoplanets collide with any and everything, while the outer disk protoplanets tend to avoid each other. We have altered the wording of this sentence to reflect this.
750: use /citep[see][]{Kokubo}
	Fixed
756: I agree that the large bodies must've originated due to mergers with other embryos, but this is not really an explanation for why the feeding zone size doesn't match the theoretical value, no? Instead it's the lack of gravitational scattering, as the authors write above. Maybe the authors can clarify specifically why oligarchic growth models predict this feeding zone size, and also why gravitational scattering is suppressed in the inner disk (due to the lack of primordial planetesimals in the inner disk?).
766: "One should note that [...]." This sentence can be deleted in my opinion.
	Removed
Figure 10:
I suggest indicating the boundary between accretion modes in this figure. >60d orbits only include 4-5 bodies. However, to me it seems like the shape of the accretion zone is qualitatively the same until ~ 20 orbits, which strengthens my view that the 60d orbit boundary is not very clear at all.
I suggest matching the x-axis limits the shown xdata.
I think "Fraction of planetesimals accreted" is a somewhat misleading description of what the plot is showing. What about: "Distribution of accreted planetesimals"?
775: The transition between smooth and unimodal seems to be happening at about 20 days to me.
Figure 11
The y-axis label overlap
I think the finding that the crossing of alpha = 0.1 in the bottom panel well matches the crossing of tilde b = 2 sqrt(3) is interesting and worth highlighting more, maybe with some vertical lines? Is there a meaning behind alpha = 0.1, i.e., is this coming from some analytical consideration? See my major comments
	TODO: Include more sims in top panel of figure 11?

6. Simplifying assumptions
6.1 Collision cross section
802: As I argued above, I'm unconvinced in this clear-cut boundary at 60 days. Maybe the authors could put a quantitative uncertainty to this number?
	The additional simulations included in figure 8, along with the difference in accretion characteristics near ~30-40d (see figures 9 and 10) suggests that the boundary lies somewhere between 40 and 70 days. This is now stated here in the text.
816: I'm not following where the factor of 15 comes from. Maybe the authors can write down the explicit proportionality used to obtain this value.
	For a fixed value of alpha, equation 4 gives a ~ r_pl ~ f. Therefore, P_orbit ~ f^{-3/2}.  This is now clarified in the text.
821: How is this expected to change with f?
	See previous comment.
843: Maybe add reference to such short period planets.
	A reference has been added to Mulders 2018.
868: I'm not sure I fully follow this statement of the collision model. See my major comment above.
	We have added a note here discussing the outcome of a potentially destructive collision model. As we mention in response to major comment #3, the local value of alpha is independent of particle size. So long as the solid mass is not ground down and removed from the system (radial drift, dust blowout, PR drag), the non-oligarchic growth mode should persist.
Figure 12:
Add a description of what green and orange means to the plot.
	A legend depicting the colors has been added to the top panel of the plot.
901: Are the populations really indistinguishable? The authors could perform for example a Kolmogorov-Smirnov test to underline this statement. If not, I would suggest softening this statement.
	A KS test yields a p-value of 1e-5 for these distributions, although excluding the handful of initial planetesimals yields a p-value of 0.1. We therefore conclude that the distribution of protoplanets are indistinguishable, although the bounce-merge model does produce a small amount of residual planetesimals. This is now stated in the text.
912: The authors perform this collisional model test very close-in where residual planetesimal populations are suppressed anyways. Maybe the authors can comment on what would change (if anything) if this test was performed in the outer parts of the disks.
	The purpose of testing the collision model at the inner part of the disk was to ensure that the delay in growth would not cause the gravitational scattering timescale to catch back up with the collision timescale (and thus cause oligarchic growth). In the outer part of the disk t_scatter >> t_collide, so a more realistic collision model would simply lengthen the timescale for embryo formation (see Wetherill + Stewart 1993, Leinhardt + Richardson 2005). We have added this discussion to the beginning of section 6.2 in the text.

### 2023-04-28 main.tex
Almost finished addressing referee comments

In the ``fiducial'' case, we give the bodies a bulk density of 3 g
cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 
10^{-3}$. \textbf{This corresponds to a radius of 341 km} These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
a factor of $\sim$ 7100, which produces $\alpha = 1$. \textbf{This corresponds to a bulk density of $4.2 \times 10^{-4}$ g cm$^{-3}$ and a radius of 6,500 km. 
Although this is most certainly unphysical, the purpose of this modification is to have a planetesimal completely fills its Hill sphere so that no strong 
gravitational scattering should occur.} To vary $\beta$, the eccentricity dispersion is increased. For the high-$
\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$. \textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk.}

\textbf{This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}

In all cases, the simulations are evolved with a base timestep of 1.7
days, which corresponds to 3\% of an orbital dynamical time
$\sqrt{a^3/G M_{*}}$. Due to the vastly differing growth timescales in
each case, a simulation is stopped when the growth of the most massive
body flattens out. In figure \ref{fig:alpha_beta}, we show the a-e
distribution of bodies in the initial (blue) and final (orange)
snapshots from each of the 4 simulations. The size of the points
indicates the relative masses of the bodies. Only \textbf{with small
$\alpha$ (case c, d)} does a residual population of dynamically hot planetesimals
develop. The lack of high eccentricity planetesimals in the large
$\alpha$ \textbf{(case a, b) simulation} suggests that most encounters result in accretion
rather than scattering. \textbf{For} large $\beta$ \textbf{(case b, d)}, the \textbf{growing} protoplanets
and end up in a dynamically cool state,
\textbf{relative} with the initial conditions. This is due to kinetic energy 
being lost as particles inelastically collide. One last point we note
is the difference between the eccentricities of protoplanets in the 
large $\alpha$, large $\beta$ \textbf{(case b)} and the small $\alpha$,
large $\beta$ \textbf{(case d) simulation}. The dynamically cooler result of the \textbf{former} case
is likely due to the dominant role that inelastic collisions play here.

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}. Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.

To investigate whether any of these planetesimal rings underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each simulation. The ratio $M/\left< m \right>$ is plotted
in \textbf{the top panel of} figure \ref{fig:alpha_beta_evo}. \textbf{Here}, a positive slope
indicates that the quantities are diverging (i.e.
the growth rate is accelerating with mass). This behavior is
evident in all four cases. Even with a large
$\beta$, where the effective collision cross section is
 nearly equal to the geometric value, runaway growth still appears to
operate. The ubiquity of the early positive trends in this figure suggests
that as bodies collide and grow, the
relative difference in gravitational focusing factors between bodies
is what drives the system towards runaway
growth, no matter how close the collision cross sections lie to the geometric value.
Although larger encounter velocities lengthen the growth
timescales, runaway growth appears to be inevitable, so long as
gravity is the dominant force in the system. For large $\alpha$
\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
\textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident}
that \textbf{the turnover in $M/\left< m \right>$} is
driven by an increase in the average mass as the planetesimal population
becomes depleted. \textbf{For small $\alpha$, one would expect that planetesimal accretion should also eventually come to a halt as
the growth timescale lengthens due to the planetesimal surface density decreasing and the residual bodies being scattered onto high
eccentricity orbits with negligible gravitational focusing factors. Many more timesteps, however, would be required to reach this point.}

@@

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
    simulation. Each curve represents a radial slice of the disk. The outermost region evolves the slowest, and is therefore 
    represented by the top curve. The dashed lines indicate radial zones interior to the 60 day orbital period boundary.\label{fig:pl_frac_time}}
\end{center}
\end{figure}

@@

\begin{table*}
\begin{center}
\caption{Summary of Full Disk Simulations}
\begin{tabular}{lccccccc} \hline \hline
Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & d & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
fdHi              & $8.37 \times 10^{-6}$ & 903,687 & 100 & 1.5 & 1.00 & 456 & 16,377  \\
fdHiSteep    & $8.37 \times 10^{-6}$ & 903,687 & 100 & 2.5 & 1.19 & 456 & 16,377  \\
fdHiShallow & $8.37 \times 10^{-6}$ & 903,687 & 100 & 0.5 & 1.08 & 456 & 16,377 \\
fdLo             & $8.37 \times 10^{-6}$ & 45,185  & 1      & 1.5 & $1.77 \times 10^{-3}$ & 3,713 & 133,651 \\ \hline
\end{tabular}\\
A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}. $m_{pl}$ and $N_{pl}$ are the initial masses and number of planetesimals. $A$ and $d$ is the initial power law normalization and slope of the solids in the disk. $M_{PP}$ is the maximum protoplanet mass at the end of the simulation and $T_{int}$ is the amount of time each simulation was integrated. $T_{int, 1}$ is the integration time scaled by a factor of $f^{2}$, which accounts for the fact that the accretion timescale has been shortened by the inflated collision cross sections.
\label{tab:sim_properties}
\end{center}
Text goes here
\end{table*}

@@

We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
the initial (contours) and final (points) state of the simulation is
shown in the orbital period-eccentricity plane. The size of the points
indicates the relative mass of the bodies. In the bottom panel, the
final masses of the bodies (in units of feeding zone size) are shown
as a function of orbital period. \textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso2} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and 
that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
within this distance.

>>>>

In the ``fiducial'' case, we give the bodies a bulk density of 3 g
cm$^{-3}$ \textbf{(for a radius of 341 km)}, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$. These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. 
To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by 
a factor of $\sim$ 7100, which produces $\alpha = 1$. \textbf{This corresponds to a bulk density of $4.2 \times 10^{-4}$ g cm$^{-3}$ and a radius of 6,500 km. 
Although this is most certainly unphysical, the purpose of this modification is to have a planetesimal completely fills its Hill sphere so that no strong 
gravitational scattering should occur.} To vary $\beta$, the eccentricity dispersion is increased. For the high-$
\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$. \textbf{This is the largest value of $\beta$ that permits a particle at 1 AU to still have an apocenter and pericenter distance that lies within the boundaries of the disk. This choice of $\beta$ places the system firmly in the $v > v_{esc}$ regime, while still allowing growth to occur in a reasonable number of timesteps.}

In all cases, the simulations are evolved with a base timestep of 1.7
days, which corresponds to 3\% of an orbital dynamical time
$\sqrt{a^3/G M_{*}}$. Due to the vastly differing growth timescales in
each case, a simulation is stopped when the growth of the most massive
body flattens out. In figure \ref{fig:alpha_beta}, we show the a-e
distribution of bodies in the initial (blue) and final (orange)
snapshots from each of the 4 simulations. The size of the points
indicates the relative masses of the bodies. Only \textbf{with small
$\alpha$ (case c, d)} does a residual population of dynamically hot planetesimals
develop. The lack of high eccentricity planetesimals \textbf{(relative to the protoplanets)} in the large
$\alpha$ \textbf{(case a, b) simulations} suggests that most encounters result in accretion
rather than scattering. \textbf{For} large $\beta$ \textbf{(case b, d)}, the \textbf{growing} protoplanets
and end up in a dynamically cool state,
\textbf{relative} with the initial conditions. This is due to kinetic energy 
being lost as particles inelastically collide. One last point we note
is the difference between the eccentricities of protoplanets in the 
large $\alpha$, large $\beta$ \textbf{(case b)} and the small $\alpha$,
large $\beta$ \textbf{(case d) simulation}. The dynamically cooler result of the \textbf{former} case
is likely due to the dominant role that inelastic collisions play here.

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four \textbf{simulations}. In addition to 
leaving fewer residual planetesimals, the large $\alpha$ \textbf{(case a, b)} simulations produce \textbf{embryos that are a factor of a few larger}. Despite the 
vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) 
appears to have no significant effect on the final distribution of masses. \textbf{For reference, the boundary between shear and dispersion-dominated 
encounters ($e_{h}$ = 1) lies around e = $4 \times 10^{-4}$ for the planetesimal mass we have chosen. The eccentricity at which $\left< v^{2} \right>^{1/2} = 
v_{esc}$ for the planetesimals is around $10^{-2}$.}

To investigate whether any of these planetesimal rings underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each simulation. The ratio $M/\left< m \right>$ is plotted
in \textbf{the top panel of} figure \ref{fig:alpha_beta_evo}. \textbf{Here}, a positive slope
indicates that the quantities are diverging (i.e.
the growth rate is accelerating with mass). This behavior is
evident in all four cases \textbf{although the small $\alpha$ simulations eventually reach a stage where the curves
 turn over as the planetesimal supply depletes.}. Even with a large
$\beta$, where the effective collision cross section is
 nearly equal to the geometric value, runaway growth still appears to
operate. The ubiquity of the early positive trends in this figure suggests
that as bodies collide and grow, the
relative difference in gravitational focusing factors between bodies
is what drives the system towards runaway
growth, no matter how close the collision cross sections lie to the geometric value.
Although larger encounter velocities lengthen the growth
timescales, runaway growth appears to be inevitable, so long as
gravity is the dominant force in the system. For large $\alpha$
\textbf{(case a, b)}, the curves in this figure eventually turn over and begin to decline.
\textbf{In the bottom panel of figure \ref{fig:alpha_beta_evo}, we separately show the evolution of
the maximum (solid lines) and mean (dashed lines) mass for each case. Here, it is evident
that the turnover in $M/\left< m \right>$ is
driven by an increase in the average mass as the planetesimal population
becomes depleted. For small $\alpha$, one would expect that planetesimal accretion should also eventually come to a halt as
the growth timescale lengthens due to the planetesimal surface density decreasing and the residual bodies being scattered onto high
eccentricity orbits with negligible gravitational focusing factors. Many more timesteps, however, would be required to reach this point.}

@@

\textbf{One should note that this choice for the gas disk profile almost certainly does not capture the wide range of possibilities in real planet-forming disks. 
On one hand, a larger initial gas surface density could act to completely remove solids via radial drift, rendering in-situ accretion of solids impossible. On the 
other hand, a more tenuous gas disk might render aerodynamic drag forces completely unimportant. In this case, the random velocity of the initial 
planetesimals should be close to their mutual escape velocity. As we showed in section \ref{sec:narrow}, the initial dynamical state of the solids seems to 
have a very minimal effect on the final outcome of planetesimal accretion. In a similar vein to \citet{hansen12}, we choose to use a MMSN-like profile for the 
gas disk and instead vary the solid surface density profile to capture the range of mechanisms that might have acted to facilitate planetesimal formation in the 
first place.}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/pl_frac_time.png}
    \caption{The time evolution of the planetesimal surface density (in units of the total solid surface density) in the fdHi 
    simulation. Each curve represents a radial slice of the disk. \textbf{The time is measured in units of the local accretion 
    timescale at the center of each radial zone. The colors represent the orbital period at the center of each zone.}\label{fig:pl_frac_time}}
\end{center}
\end{figure}

@@

\begin{table*}
\begin{center}
\caption{Summary of Full Disk Simulations}
\begin{tabular}{lccccccc} \hline \hline
Simulation Name & $m_{pl} [M_{\earth}]$ &$N_{pl}$ & A & $\delta$ & $M_{PP}  [M_{\earth}]$ & $T_{int} [yr]$ & $T_{int, 1} [yr]$ \\ \hline
fdHi              & $8.37 \times 10^{-6}$ & 903,687 & 100 & 1.5 & 1.00 & 456 & 16,377  \\
fdHiSteep    & $8.37 \times 10^{-6}$ & 903,687 & 100 & 2.5 & 1.19 & 456 & 16,377  \\
fdHiShallow & $8.37 \times 10^{-6}$ & 903,687 & 100 & 0.5 & 1.08 & 456 & 16,377 \\
fdLo             & $8.37 \times 10^{-6}$ & 45,185  & 1      & 1.5 & $1.77 \times 10^{-3}$ & 3,713 & 133,651 \\ \hline
\end{tabular}\\
A summary of the four `full disk' simulations presented in section \ref{sec:fulldisk}. $m_{pl}$ and $N_{pl}$ are the initial masses and number of planetesimals. $A$ and $d$ is the initial power law normalization and slope of the solids in the disk. $M_{PP}$ is the maximum protoplanet mass at the end of the simulation and $T_{int}$ is the amount of time each simulation was integrated. $T_{int, 1}$ is the integration time scaled by a factor of $f^{2}$, which accounts for the fact that the accretion timescale has been shortened by the inflated collision cross sections.
\label{tab:sim_properties}
\end{center}
Text goes here
\end{table*}

@@

We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
the initial (contours) and final (points) state of the simulation is
shown in the orbital period-eccentricity plane. The size of the points
indicates the relative mass of the bodies. In the bottom panel, the
final masses of the bodies (in units of feeding zone size) are shown
as a function of orbital period. \textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and 
that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
within this distance.
